Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Add more information to study design

@@

Firstly, we will deal with a large volume of tickets and information extracted 
from software projects and the tools that revolve around them, such as issue 
trackers and version control systems. Thus, \emph{data quality} is an important 
topic that needed to be explored in order to infer appropriate conclusions.

>>>>

Firsly, we will deal with a large volume of tickets and information extracted 
from software projects and the tools that revolve around them, such as issue 
trackers and version control systems. Thus, \emph{data quality} is an important 
topic that needed to be explored in order to infer appropriate conclusions.

@@
